Slovene NLTK Tagger

### 2012-01-07 paper/paper.tex
Added my email to paper.
Added unfinished section Brill tagger.

\title{Slovene NLTK Tagger}
\author{
	Niko Colnerič \\
	\footnotesize Faculty of Computer and \\
	\footnotesize Information Science \\
	\footnotesize University of Ljubljana \\
	\footnotesize \texttt{niko.colneric@gmail.com} \\
	\and
	Nejc Banič \\
	\footnotesize Faculty of Computer and \\
	\footnotesize Information Science \\
	\footnotesize University of Ljubljana \\
	\footnotesize \texttt{MAIL@} \\
}

@@

\subsection{Brill tagger} %BANIČ
\textit{TODO - BANIČ}
Banič glej ta link : nltk.googlecode.com/svn/trunk/doc/book/ch05.html
poglavje 5.6
\subsection{Naive Bayes tagger} %BANIČ
\textit{TODO - BANIČ}

>>>>

\title{Slovene NLTK Tagger}
\author{
	Niko Colnerič \\
	\footnotesize Faculty of Computer and \\
	\footnotesize Information Science \\
	\footnotesize University of Ljubljana \\
	\footnotesize \texttt{niko.colneric@gmail.com} \\
	\and
	Nejc Banič \\
	\footnotesize Faculty of Computer and \\
	\footnotesize Information Science \\
	\footnotesize University of Ljubljana \\
	\footnotesize \texttt{banic.nejc@gmail.com} \\
}

@@

\subsection{Brill tagger} %BANIČ
\textit{TODO - BANIČ}
Banič glej ta link : nltk.googlecode.com/svn/trunk/doc/book/ch05.html
poglavje 5.6
The Brill tagger is another part-of-speech tagger and was first described by Eric Brill in 1993. Before trying to explain it, we must address issues with all n-gram taggers (e.g. \textit{Trigram tagger}).

First issue with n-gram tagger is size of their n-gram table. If we wan't to use the tagger on mobile computing device, compromise must be taken between performance and model size.

A second issue with n-gram tagger is that the only information it considers from prior context is tags. This is not practical because words themselves are useful information also. Therefore n-gram taggers are impractical models to be used to identify words in context.

To bypass these problems we can use \textit{Brill tagger}. It can be summarised as an transformation-basede learning and performs very well using models that are just a fraction of the size of n-gram taggers.

The general idea is very simple: guess the tag of each word, then go back and fix the mistakes. In this way, a Brill tagger successively transforms a bad tagging of a text into a better one. As with n-gram tagging, this is a supervised learning method, since we need annotated training data to figure out whether the tagger's guess is a mistake or not. However, unlike n-gram tagging, it does not count observations but compiles a list of transformational correction rules.

\subsection{Naive Bayes tagger} %BANIČ
\textit{TODO - BANIČ}
